---
title: "Anatomy 3"
author: "Marco D'Agostino"
date: "06/05/2022"
output:
  html_document:
    smart: FALSE
    code_folding: hide #  Cache le code  
    collapsed: yes # Crée un document unique 
    fig_caption: no # Figures encapsulées ? 
    fig_height: 5 # Hauteur par défaut des figures
    fig_width: 6 # Largeur par défaut des figures
    highlight: tango # Style de mise en valeur du code
    number_sections: yes # Ajout table des matières 
    theme: united  # Style du document
    toc: yes # Table des matiere ?
    toc_depth: 3  # Profondeur table des matières<
    toc_float: yes # Table des matières flottante a
editor_options:
  chunk_output_type: inline
---

```{r setup, include=FALSE}
# R Chunks options
knitr::opts_chunk$set(comment="")

setwd(dirname(rstudioapi::getActiveDocumentContext()$path)) # Set working directory to the current file
rm(list = ls())

# Packages
require(readxl)
require(pander)
require(dplyr)
require(car)
require(Hmisc)
require(EnvStats)
require(emmeans)
require(visreg)
require(sjplot)
require(FactoMineR)
require(factoextra)
require(ggplot2)
library(viridis)
library(hrbrthemes)
require(knitr)
require(gridExtra)
require(extrafont)
require(sjPlot)
require(epitools)
require(corrplot)
require(NbClust)
require(pastecs)
require(kohonen)
require(data.table)
require(tidyverse)
library("SciViews")

library(sp)
library(xml2)
library(plyr)
library(deldir)
library(alphahull)
library(cowplot)
library(retistruct)
library(Hmisc)

# Path to data
q_path <- "Data/Quantification/clean/"

# Load functions
source("functions.R")

# Fonts
windowsFonts(A = windowsFont("Cambria"))
```

# Import data (1)

Merge all data of cross sections into one database

```{r}
anatomy_DB <- data.frame(cs_id = c(),
                         name = c(),
                         type = c(),
                         value = c())

# Make a list of all files names
list <- list.files(path = q_path, pattern = "xlsx")

for(k in seq(1:length(list))){
  
    

    path = paste0(q_path, list[k])

    # Generate the row of ids
    cs_id <- extract_ids(list, k)
    
    print(paste0("Initializing incorporation of data from cross section ", cs_id$plant_id, " , segment", cs_id$segment))

    # load file with the path
    file <- read_xlsx(path)
    sheets <- excel_sheets(path)

    # Process each sheet
    for(i in sheets){
      
      if(i == "Layers"){
        #print("This is the layer")
        temp_file <- read_xlsx(path, sheet = i)
        
        for (p in seq(1:length(temp_file$id))) {
        
          temp_df_layer <- data.frame(name = temp_file$name[p],
                                      type = "nLayers",
                                      value = temp_file$layers[p])
          temp_df_layer2 <- merge(cs_id, temp_df_layer)
          anatomy_DB <- rbind(anatomy_DB, temp_df_layer2)
          
          temp_df_radius <- data.frame(name = temp_file$name[p],
                                       type = "radius",
                                       value = temp_file$radius[p])
          temp_df_radius2 <- merge(cs_id, temp_df_radius)
          anatomy_DB <- rbind(anatomy_DB, temp_df_radius2)
          }
          
        }
        
      else{
        temp_file <- read_xlsx(path, sheet = i)
        name = i
  
        # Process each params per sheet
        types = colnames(temp_file) # we take from 2 because the first column is the id
  
        for (j in seq(from = 2,
                      to = length(types),
                      by = 1)) {
  
                                  temp_df <- data.frame(value = temp_file[[j]])
                                  temp_df$name = i
                                  temp_df$type = types[j]
                                  # temp_df$measure_id = seq(from = 1,
                                  #                          to = length(temp_df$value),
                                  #                          by = 1)
                          
                                  temp_df2 <- merge(cs_id, temp_df)
                                  anatomy_DB <- rbind(anatomy_DB, temp_df2)
          
        }
      # end of j for
    }
    # end of else
    } 
    # end of i
}
# end of k for

Plants <- read.csv("Data/Plants.csv")
Plants <- subset(Plants, select = -c(X, repetition))
anatomy_DB <- merge(x = anatomy_DB, y = Plants,
                      by = "plant_id")

Genotypes <- read.csv("Data/Genotypes.csv")
Genotypes <- subset(Genotypes, select = -X)
anatomy_DB <- merge(x = anatomy_DB, y = Genotypes[,c(2,3)],
                      by = "gen_id")

write.csv(anatomy_DB, "Data/Anatomy_full.csv")
```

# Import data (2)

If previous chunk has already been executed, we simply can load csv :

```{r}
anatomy_DB <- read.csv("Data/Anatomy_full.csv")
anatomy_DB$value <- as.numeric(anatomy_DB$value)
anatomy_DB <- subset(anatomy_DB, select = -X)

anatomy_full <- read.csv("Data/Anatomy.csv")
anatomy_full <- subset(anatomy_full, select = -X)
```

some manipulations :

```{r}
anatomy_full <- anatomy_full %>% filter(segment != "S1")
anatomy_full$segment2 <- 1
anatomy_full$segment2[anatomy_full$segment == "S2"] = 2
anatomy_full$segment2[anatomy_full$segment == "S3"] = 3
anatomy_full$segment2[anatomy_full$segment == "S4"] = 4

```

# GGPlot function

```{r}
anatomy_plot <- function(Data = data,
                         Title = title){
  
  ggplot(data = Data, aes(x = segment, y = value, fill = gen_id)) +
    geom_point(aes(color = gen_id)) +
    geom_boxplot() + 
    
    # stat_summary(fun.y = median, geom = "line", 
    #              aes(group = gen_id, color = gen_id),
    #              position = position_dodge(width = 0.9)) +
    
    #facet_wrap(~segment, ncol = 4) +
    theme_bw() +
    # scale_fill_manual(values = c("G" = "coral1", "A" =  "turquoise3")) +
    #geom_jitter(color="black", size=0.4, alpha=0.9) + # Add points
      
    theme(axis.line = element_line(color='black'),
        
          # Remove grid
          plot.background = element_blank(),
          panel.grid.major = element_blank(),
          panel.grid.minor = element_blank(),
          
          # Change font
          text = element_text(family = "A"),
          
          # Remove x ticks
          #axis.text.x=element_blank(),
          #axis.ticks.x=element_blank(),
          
          # Remove legend title
          #legend.title=element_blank()
          
          # Remove legend
          #legend.position="none"
          
          # Remove panel borders 
          #panel.border = element_blank()
          ) +
    ggtitle(Title)
  
  
  
}
```

## 1. Xylem

```{r}
xylem_stats <- anatomy_full %>% filter(name == "xylem")

xylem_n_files <- xylem_stats %>% filter(type == "n_files") 
xylem_max_size <- xylem_stats %>% filter(type == "max_size")
xylem_mean_size <- xylem_stats %>% filter(type == "mean_size")


anatomy_plot(xylem_n_files, Title = "Xylem | n_files")
anatomy_plot(xylem_max_size, Title = "Xylem | max_size")
anatomy_plot(xylem_mean_size, Title = "Xylem | mean_size")
```

### Investigate the total xylem area

```{r}
xylem <- subset(xylem_max_size, select = c("plant_id", "gen_id", "segment", "gtype", "segment2"))

xylem$MaxSize <- xylem_max_size$value
xylem$MeanSize <- xylem_mean_size$value
xylem$nFiles <- xylem_n_files$value

xylem$TotArea <- xylem$MeanSize*xylem$nFiles
xylem$TotAreaLog <- log10(xylem$TotArea)

# GGPLOT
ggplot(data = xylem,
       aes(x = segment, 
           y = TotAreaLog,
           # color = gen_id,
           fill = gen_id)) +
  geom_point(aes(color = gen_id)) +
  geom_boxplot() +
  
  theme_bw() +
  
  theme(axis.line = element_line(color='black'),
        
          # Remove grid
          plot.background = element_blank(),
          panel.grid.major = element_blank(),
          panel.grid.minor = element_blank(),
          
          # Change font
          text = element_text(family = "A"))
  
```

### Xylem tot area along the root

```{r}
ggplot(data = xylem,
       aes(x = segment2, 
           y = TotAreaLog,
           # color = gen_id,
           fill = gen_id)) +
  
  # POINTS
  geom_point(aes(x = segment2,
                 y = TotAreaLog,
                 color = gen_id),
             color = "grey") +

  # geom_point(aes(x = segment2,
  #                y = SteleLD,
  #                color = gen_id),
  #            color = "grey") +
  
  # CURVES
  geom_smooth(aes(x = segment2,
                y = TotAreaLog,
                color = gen_id),
              se = T,
              alpha = 0.1,
              method = lm,
              formula = y ~ x
              ) +
  
  # geom_smooth(aes(x = segment2,
  #                 y = SteleLD,
  #                 color = gen_id
  #                 ),
  #             linetype = "twodash",
  #             se = T,
  #             #method = lm,
  #             alpha = 0.1) +

  
  # geom_boxplot(aes(factor(segment2))) +
  
  theme_bw() +
  theme(axis.line = element_line(color='black'),
        
          # Remove grid
          plot.background = element_blank(),
          panel.grid.major = element_blank(),
          panel.grid.minor = element_blank(),
          
          # Change font
          text = element_text(family = "A"))
```

### Analytical stats

```{r}
xylem2 <- xylem %>% filter(segment == "S2")
xylem3 <- xylem %>% filter(segment == "S3")
xylem4 <- xylem %>% filter(segment == "S4")
```

1)  nFiles

```{r}
# n_files
xylem_lm1 <- lm(data = xylem,
                formula = nFiles ~ segment + gen_id)

summary(xylem_lm1)
anova(xylem_lm1)
```

Conclusions : segment have a significant effect. Genotype not really

2)  Mean_size

```{r}
xylem_lm2 <- lm(data = xylem,
                formula = MeanSize ~ segment + gen_id)

summary(xylem_lm2)
anova(xylem_lm2)
```

seems that gen_id not signific for all segements, but for separated segments?

```{r}

print("SEGMENT 2")
xylem_lm3a <- lm(data = xylem2,
                 formula = MeanSize ~ gen_id)

summary(xylem_lm3a)
anova(xylem_lm3a)

##################################################################
print("SEGMENT3")
xylem_lm3b <- lm(data = xylem3,
                 formula = MeanSize ~ gen_id)

summary(xylem_lm3b)
anova(xylem_lm3b)

##################################################################
print("SEGMENT4")
xylem_lm3c <- lm(data = xylem4,
                 formula = MeanSize ~ gen_id)

summary(xylem_lm3c)
anova(xylem_lm3c)

##################################################################
```

seems that gen_id has effect for 4 and 3 segments

3)  Tot Area

```{r}
xylem_lm4 <- lm(data = xylem,
                formula = TotAreaLog ~ segment + gen_id)

summary(xylem_lm4)
anova(xylem_lm4)

```

Xylem tot area signific different between gen_id and segments !!

## 2. Stele

```{r}
stele_stats <- anatomy_full %>% filter(name == "stele")

stele_cell_diameter <- stele_stats %>% filter(type == "cell_diameter") 
stele_layer_diameter <- stele_stats %>% filter(type == "layer_diameter")
stele_mean_size <- stele_stats %>% filter(type == "mean_size")
stele_n_layers <- stele_stats %>% filter(type == "n_layers")
stele_SD <- stele_stats %>% filter(type == "SD")
stele_totarea <- stele_stats %>% filter(type == "totarea")

anatomy_plot(stele_cell_diameter, Title = "Stele | cell_diameter")
anatomy_plot(stele_layer_diameter, Title = "Stele | layer_diameter")
anatomy_plot(stele_mean_size, Title = "Stele | mean_size")
anatomy_plot(stele_n_layers, Title = "Stele | n_layers")
anatomy_plot(stele_SD, Title = "Stele | SD")
anatomy_plot(stele_totarea, Title = "Stele | totarea")
```

TotAreaLog

```{r}
Stele <- subset(stele_cell_diameter, select = c("plant_id", "gen_id", "segment", "gtype"))
Stele$CellDiameter <- stele_cell_diameter$value
Stele$LayerDiameter <- stele_layer_diameter$value
Stele$MeanSize <- stele_mean_size$value
Stele$nLayers <- stele_n_layers$value
Stele$SD <- stele_SD$value
Stele$TotArea <- stele_totarea$value

Stele$TotAreaLog <- log10(Stele$TotArea)

# GGPLOT
ggplot(data = Stele,
       aes(x = segment, 
           y = TotAreaLog,
           # color = gen_id,
           fill = gen_id)) +
  geom_point(aes(color = gen_id)) +
  geom_boxplot() +
  
  theme_bw() +
  
  theme(axis.line = element_line(color='black'),
        
          # Remove grid
          plot.background = element_blank(),
          panel.grid.major = element_blank(),
          panel.grid.minor = element_blank(),
          
          # Change font
          text = element_text(family = "A"))
```

Analytical stats

1)  TotAreaLog

```{r}
stele_lm1 <- lm(data = Stele,
                formula = TotAreaLog ~ segment + gen_id)

summary(stele_lm1)
anova(stele_lm1)
```

2)  Layer diameter

```{r}
stele_lm2 <- lm(data = Stele,
                formula = LayerDiameter ~ segment + gen_id)

summary(stele_lm2)
anova(stele_lm2)
```

3)  Mean cell size

```{r}
stele_lm3 <- lm(data = Stele,
                formula = MeanSize ~ segment + gen_id)

summary(stele_lm3)
anova(stele_lm3)
```

## 3. Phloem

```{r}
phloem_stats <- anatomy_full %>% filter(name == "phloem")

phloem_n_files <- phloem_stats %>% filter(type == "n_files") 
phloem_max_size <- phloem_stats %>% filter(type == "max_size")
phloem_proportion <- phloem_stats %>% filter(type == "proportion")

anatomy_plot(phloem_n_files, Title = "Phloem | n_files")
anatomy_plot(phloem_max_size, Title = "Phloem | max_size")
anatomy_plot(phloem_proportion, Title = "Phloem | proportion")
```

Phloem analytical stats

```{r}
Phloem <- subset(phloem_n_files, select = c("plant_id", "gen_id", "segment", "gtype"))
Phloem$NFiles <- phloem_n_files$value
Phloem$MaxSize  <- phloem_max_size$value
Phloem$Proportion  <- phloem_proportion$value
```

NFiles

```{r}
phloem_lm1 <- lm(data = Phloem,
                 formula = NFiles ~ segment + gen_id)
summary(phloem_lm1)
anova(phloem_lm1)
```

MaxSize

```{r}
phloem_lm2 <- lm(data = Phloem,
                 formula = MaxSize ~ segment + gen_id)
summary(phloem_lm2)
anova(phloem_lm2)
```

Proportion

```{r}
phloem_lm3 <- lm(data = Phloem,
                 formula = Proportion ~ segment + gen_id)
summary(phloem_lm3)
anova(phloem_lm3)
```

## 4. Pericycle

```{r}
pericycle_stats <- anatomy_full %>% filter(name == "pericycle")

pericycle_cell_diameter <- pericycle_stats %>% filter(type == "cell_diameter") 

anatomy_plot(pericycle_cell_diameter, Title = "Pericycle | cell_diameter")
```

Anatomical stats

```{r}
Pericycle <- subset(pericycle_cell_diameter, select = c("plant_id", "gen_id", "segment", "gtype"))
Pericycle$CellDiameter <- pericycle_cell_diameter$value

pericycle_lm <- lm(data = Pericycle,
                   formula = CellDiameter ~ segment + gen_id)

summary(pericycle_lm)
anova(pericycle_lm)
```

5.  Endodermis

```{r}
endodermis_stats <- anatomy_full %>% filter(name == "endodermis")

endodermis_barrier <- endodermis_stats %>% filter(type == "barrier")
endodermis_cell_diameter <- endodermis_stats %>% filter(type == "cell_diameter")

anatomy_plot(endodermis_barrier, Title = "Endodermis | barrier")
anatomy_plot(endodermis_cell_diameter, Title = "Endodermis | cell_diameter")
```

```{r}
Endodermis <- subset(endodermis_barrier, select = c("plant_id", "gen_id", "segment", "gtype"))
Endodermis$Barriers <- endodermis_barrier$value
Endodermis$CellDiameter  <- endodermis_cell_diameter$value


print("Cell Diameter")
endo_lm1 <- lm(data = Endodermis,
               formula = CellDiameter ~ segment + gen_id)

summary(endo_lm1)
anova(endo_lm1)


```

## 6. Cortex

```{r}
cortex_stats <- anatomy_full %>% filter(name == "cortex")

cortex_n_layers <- cortex_stats %>% filter(type == "n_layers") 
cortex_cell_diameter <- cortex_stats %>% filter(type == "cell_diameter")

anatomy_plot(cortex_n_layers, Title = "Cortex | n_layers")
anatomy_plot(cortex_cell_diameter, Title = "Cortex | cell_diameter")
```

Layer Diameter = cell_diameter \* nLayers

```{r}
Cortex <- subset(cortex_cell_diameter, select = c("plant_id", "gen_id", "segment", "gtype","segment2"))
Cortex$nLayers <- cortex_n_layers$value
Cortex$CellDiameter <- cortex_cell_diameter$value

Cortex$LayerDiameter <- Cortex$CellDiameter*Cortex$nLayers

# GGPLOT
ggplot(data = Cortex,
       aes(x = segment, 
           y = LayerDiameter,
           # color = gen_id,
           fill = gen_id)) +
  geom_point(aes(color = gen_id)) +
  geom_boxplot() +
  
  theme_bw() +
  
  theme(axis.line = element_line(color='black'),
        
          # Remove grid
          plot.background = element_blank(),
          panel.grid.major = element_blank(),
          panel.grid.minor = element_blank(),
          
          # Change font
          text = element_text(family = "A"))

```

Layer diameter curve graph

```{r}
ggplot(data = Cortex,
       aes(x = segment2, 
           y = LayerDiameter,
           # color = gen_id,
           fill = gen_id)) +
  
  # POINTS
  geom_point(aes(x = segment2,
                 y = LayerDiameter,
                 color = gen_id),
             color = "grey") +

  # geom_point(aes(x = segment2,
  #                y = SteleLD,
  #                color = gen_id),
  #            color = "grey") +
  
  # CURVES
  geom_smooth(aes(x = segment2,
                y = LayerDiameter,
                color = gen_id),
              se = T,
              alpha = 0.1,
              method = lm,
              formula = y ~ x + I(x^2)
              ) +
  
  # geom_smooth(aes(x = segment2,
  #                 y = SteleLD,
  #                 color = gen_id
  #                 ),
  #             linetype = "twodash",
  #             se = T,
  #             #method = lm,
  #             alpha = 0.1) +

  
  # geom_boxplot(aes(factor(segment2))) +
  
  theme_bw() +
  theme(axis.line = element_line(color='black'),
        
          # Remove grid
          plot.background = element_blank(),
          panel.grid.major = element_blank(),
          panel.grid.minor = element_blank(),
          
          # Change font
          text = element_text(family = "A"))
```

Cortex analytical stats

1)  Cell diameter

```{r}
cortex_lm1 <- lm(data = Cortex,
                 formula = CellDiameter ~ segment + gen_id)

summary(cortex_lm1)
anova(cortex_lm1)
```

2)  nLayers

```{r}
cortex_lm2 <- lm(data = Cortex,
                 formula = nLayers ~ segment + gen_id)

summary(cortex_lm2)
anova(cortex_lm2)
```

3)  LayerDiameter

```{r}
cortex_lm3 <- lm(data = Cortex,
                 formula = LayerDiameter ~ segment + gen_id + segment:gen_id)

summary(cortex_lm3)
anova(cortex_lm3)
```

## Compare cortex and stele layer diameter

```{r}
SteleCortex <- subset(Stele, select = c("plant_id", "gen_id", "segment", "gtype"))
SteleCortex$SteleLD <- Stele$LayerDiameter
SteleCortex$CortexLD <- Cortex$LayerDiameter

# Set segment as numeric
SteleCortex$segment2 <- 1
SteleCortex$segment2[SteleCortex$segment == "S2"] = 2
SteleCortex$segment2[SteleCortex$segment == "S3"] = 3
SteleCortex$segment2[SteleCortex$segment == "S4"] = 4

# GGPLOT
ggplot(data = SteleCortex,
       aes(x = segment2, 
           y = CortexLD,
           # color = gen_id,
           fill = gen_id)) +
  
  # POINTS
  # geom_point(aes(x = segment2,
  #                y = CortexLD,
  #                color = gen_id),
  #            color = "grey") +
  # 
  # geom_point(aes(x = segment2,
  #                y = SteleLD,
  #                color = gen_id),
  #            color = "grey") +
  
  # CURVES
  geom_smooth(aes(x = segment2,
                y = CortexLD,
                color = gen_id),
              se = T,
              alpha = 0.1,
              method = lm,
              formula = y ~ x + I(x^2),
              ) +
  
  geom_smooth(aes(x = segment2,
                  y = SteleLD,
                  color = gen_id
                  ),
              linetype = "twodash",
              se = T,
              method = lm,
              formula = y ~ x + I(x^2),
              alpha = 0.1) +

  
  # geom_boxplot(aes(factor(segment2))) +
  
  theme_bw() +
  theme(axis.line = element_line(color='black'),
        
          # Remove grid
          plot.background = element_blank(),
          panel.grid.major = element_blank(),
          panel.grid.minor = element_blank(),
          
          # Change font
          text = element_text(family = "A"))
```

## Compare radius

```{r}
SteleRadius <- anatomy_DB %>% filter(name == "stele" & type == "radius")
CortexRadius <- anatomy_DB %>% filter(name == "cortex" & type == "radius")

RadiusStats <- subset(SteleRadius, select = c("plant_id", "gen_id", "segment", "gtype"))
RadiusStats$SteleRadius <- SteleRadius$value
RadiusStats$CortexRadius <- CortexRadius$value

# Set segment as numeric
RadiusStats$segment2 <- 1
RadiusStats$segment2[RadiusStats$segment == "S2"] = 2
RadiusStats$segment2[RadiusStats$segment == "S3"] = 3
RadiusStats$segment2[RadiusStats$segment == "S4"] = 4
```

Plot

```{r}
# GGPLOT
ggplot(data = RadiusStats,
       aes(x = segment2, 
           y = SteleRadius,
           # color = gen_id,
           fill = gen_id)) +
  
  # POINTS
  # geom_point(aes(x = segment2,
  #                y = SteleRadius,
  #                color = gen_id),
  #            color = "grey") +
  # 
  # geom_point(aes(x = segment2,
  #                y = CortexRadius,
  #                color = gen_id),
  #            color = "grey") +
  
  # CURVES
  geom_smooth(aes(x = segment2,
                y = SteleRadius,
                color = gen_id),
              se = T,
              alpha = 0.1,
              method = lm,
              formula = y ~ x + I(x^2),
              ) +
  
  geom_smooth(aes(x = segment2,
                  y = CortexRadius,
                  color = gen_id
                  ),
              linetype = "twodash",
              se = T,
              method = lm,
              formula = y ~ x + I(x^2),
              alpha = 0.1) +
  
  facet_wrap(~ gen_id) +
  
  
  # geom_boxplot(aes(factor(segment2))) +
  
  theme_bw() +
  theme(axis.line = element_line(color='black'),
        
          # Remove grid
          plot.background = element_blank(),
          panel.grid.major = element_blank(),
          panel.grid.minor = element_blank(),
          
          # Change font
          text = element_text(family = "A"))
```

## 7. Exodermis

```{r}
exodermis_stats <- anatomy_full %>% filter(name == "exodermis")

exodermis_barrier <- exodermis_stats %>% filter(type == "barrier")
exodermis_cell_diameter <- exodermis_stats %>% filter(type == "cell_diameter")

anatomy_plot(exodermis_barrier, Title = "Exodermis | barrier")
anatomy_plot(exodermis_cell_diameter, Title = "Exodermis | cell_diameter")
```
stats 

```{r}
exodermis <- subset(exodermis_barrier, select = c("plant_id", "gen_id", "segment", "gtype"))
exodermis$barrier <- exodermis_barrier$value
exodermis$CellDiameter <- exodermis_cell_diameter$value

exo_lm <- lm(data = exodermis,
             formula = CellDiameter ~ segment + gen_id)

summary(exo_lm)
anova(exo_lm)
```


## 8. Epidermis

```{r}
epidermis_stats <- anatomy_full %>% filter(name == "epidermis")

epidermis_cell_diameter <- epidermis_stats %>% filter(type == "cell_diameter")

anatomy_plot(epidermis_cell_diameter, Title = "Epidermis | cell_diameter")
```

stats

```{r}
epidermis <- subset(epidermis_stats, select = c("plant_id", "gen_id", "segment", "gtype"))
epidermis$CellDiameter <- epidermis_cell_diameter$value

epi_lm <- lm(data = epidermis,
             formula = CellDiameter ~ segment + gen_id)

summary(epi_lm)
anova(epi_lm)
```


# PCA

Let's make a biiiiig file to do a PCA

First we will classify parameters and put an simple id to it

```{r}
# temp <- anatomy_full %>% filter(id == 1)
# temp <- subset(temp, select = c(name,type))
# temp$param_id <- 0
# 
# for(i in seq(1:length(temp$name))){
#   temp[i,]$param_id <- paste0("param_",i)
# }
# 
# Param_table <- temp
# write.csv(Param_table, "Data/Param_table.csv")
```

Import param table

```{r}
Param_table <- read.csv("Data/Param_table.csv")
Param_table <- subset(Param_table, select = -X)
```

Import CrossSections

```{r}
CrossSections <- read.csv("Data/CrossSections.csv")
CrossSections <- subset(CrossSections, select = -X)
```

```{r}
# test <- merge(anatomy_full, Param_table, by = c("name", "type"))
# test <- merge(test, CrossSections, by = c("plant_id", "segment", "cut","zoom", "repetition"))
# 
# test <- subset(test, select = c(CS_id, param_id, value))
# 
# Anatomy_table <- test
# write_csv(Anatomy_table, "Data/Anatomy_table.csv")

Anatomy_table <- read.csv("Data/Anatomy_table.csv")
```

Create PCA table

```{r}
PCA_table <- data.frame(CS_id = c())



####

for(i in unique(Anatomy_table$CS_id)){
  subtemp <- Anatomy_table %>% filter(CS_id == i)
  temp <- data.frame(CS_id = i,
                     param_1 = subtemp$value[subtemp$param_id == "param_1"],
                     param_2 = subtemp$value[subtemp$param_id == "param_2"],
                     param_3 = subtemp$value[subtemp$param_id == "param_3"],
                     param_4 = subtemp$value[subtemp$param_id == "param_4"],
                     param_5 = subtemp$value[subtemp$param_id == "param_5"],
                     param_6 = subtemp$value[subtemp$param_id == "param_6"],
                     param_7 = subtemp$value[subtemp$param_id == "param_7"],
                     param_8 = subtemp$value[subtemp$param_id == "param_8"],
                     param_9 = subtemp$value[subtemp$param_id == "param_9"],
                     param_10 = subtemp$value[subtemp$param_id == "param_10"],
                     param_11 = subtemp$value[subtemp$param_id == "param_11"],
                     param_12 = subtemp$value[subtemp$param_id == "param_12"],
                     param_13 = subtemp$value[subtemp$param_id == "param_13"],
                     param_14 = subtemp$value[subtemp$param_id == "param_14"],
                     param_15 = subtemp$value[subtemp$param_id == "param_15"],
                     param_16 = subtemp$value[subtemp$param_id == "param_16"],
                     param_17 = subtemp$value[subtemp$param_id == "param_17"],
                     param_18 = subtemp$value[subtemp$param_id == "param_18"],
                     param_19 = subtemp$value[subtemp$param_id == "param_19"],
                     param_20 = subtemp$value[subtemp$param_id == "param_20"],
                     param_21 = subtemp$value[subtemp$param_id == "param_21"],
                     param_22 = subtemp$value[subtemp$param_id == "param_22"],
                     param_23 = subtemp$value[subtemp$param_id == "param_23"],
                     param_24 = subtemp$value[subtemp$param_id == "param_24"],
                     param_25 = subtemp$value[subtemp$param_id == "param_25"],
                     param_26 = subtemp$value[subtemp$param_id == "param_26"],
                     param_27 = subtemp$value[subtemp$param_id == "param_27"],
                     param_28 = subtemp$value[subtemp$param_id == "param_28"],
                     param_29 = subtemp$value[subtemp$param_id == "param_29"],
                     param_30 = subtemp$value[subtemp$param_id == "param_30"],
                     param_31 = subtemp$value[subtemp$param_id == "param_31"],
                     param_32 = subtemp$value[subtemp$param_id == "param_32"],
                     param_33 = subtemp$value[subtemp$param_id == "param_33"],
                     param_34 = subtemp$value[subtemp$param_id == "param_34"],
                     param_35 = subtemp$value[subtemp$param_id == "param_35"],
                     param_36 = subtemp$value[subtemp$param_id == "param_36"])


  PCA_table <- rbind(PCA_table, temp)
}

write_csv(PCA_table, "Data/PCA_table.csv")
```

# PCA

```{r}
# Load data
PCA_table <- read_csv("Data/PCA_table.csv")

# Process to PCA
PCA_table$CS_id <- as.factor(PCA_table$CS_id)
Group = PCA_table$CS_id
PCA_table <- subset(PCA_table, select = -CS_id)
PCA_table <- subset(PCA_table, select = -c(param_1,
                                           param_2,
                                           param_3,
                                           param_4,
                                           param_5,
                                           param_9,
                                           param_15,
                                           param_17,
                                           param_19,
                                           param_20,
                                           param_22,
                                           param_23,
                                           param_25,
                                           param_26,
                                           param_28,
                                           param_29,
                                           param_30,
                                           param_31,
                                           param_34,
                                           param_35
                                           ))

# PCA
pairs(PCA_table, col = Group, main = "Scatter Plot", cex=0.5, pch = 20)

resACP <- prcomp(PCA_table, center = TRUE, scale = TRUE)
```

```{r}
round(get_eig(resACP), 4)
summary(resACP)
```

```{r}
resACP$rotation[,1:2]

var <-get_pca_var(resACP)
var$cor[,1:2]

fviz_pca_var(resACP, axes = c(1,2))
```

```{r}
fviz_pca_ind(resACP, axes=c(1,2), geam.ind="point", col.ind=Group, legend.title="Marque", addEllipses = TRUE)
```

```{r}
res.dist <- get_dist(PCA_table, method = "euclidean")
fviz_dist(res.dist,order=FALSE)
```

```{r}
library(GGally)

ggcorr(data = PCA_table)
```

# Xylem topology

```{r}
xylem_topo <- anatomy_DB %>% filter(name == "Xylem", type == c("XM", "YM")) 

xylem_topo$repetition <- as.numeric(xylem_topo$repetition)

xylem_topo2 <- merge(xylem_topo,
                     CrossSections,
                     by = c("plant_id", "segment", "cut","zoom","repetition"))


```
