---
title: "Anatomy 2"
author: "Marco D'Agostino"
date: "06/05/2022"
output:
  html_document:
    smart: FALSE
    code_folding: hide #  Cache le code  
    collapsed: yes # Crée un document unique 
    fig_caption: no # Figures encapsulées ? 
    fig_height: 5 # Hauteur par défaut des figures
    fig_width: 6 # Largeur par défaut des figures
    highlight: tango # Style de mise en valeur du code
    number_sections: yes # Ajout table des matières 
    theme: united  # Style du document
    toc: yes # Table des matiere ?
    toc_depth: 3  # Profondeur table des matières<
    toc_float: yes # Table des matières flottante a
editor_options:
  chunk_output_type: html
---

```{r echo=TRUE,include=FALSE}
# R Chunks options
knitr::opts_chunk$set(comment="")

setwd(dirname(rstudioapi::getActiveDocumentContext()$path)) # Set working directory to the current file
rm(list = ls())

# Packages
require(readxl)
require(pander)
require(dplyr)
require(car)
require(Hmisc)
require(EnvStats)
require(emmeans)
require(visreg)
require(sjplot)
require(FactoMineR)
require(factoextra)
require(ggplot2)
library(viridis)
library(hrbrthemes)
require(knitr)
require(gridExtra)
require(extrafont)
require(sjPlot)
require(epitools)
require(corrplot)
require(NbClust)
require(pastecs)
require(kohonen)
require(data.table)
require(tidyverse)
library("SciViews")

library(sp)
library(xml2)
library(plyr)
library(deldir)
library(alphahull)
library(cowplot)
library(retistruct)
library(Hmisc)


# Load functions
source("functions.R")

# Fonts
windowsFonts(A = windowsFont("Cambria"))
```

# 1. Data preparation for GRANAR

## Option 1 : Create data from quantifications

Set directory to the folder of the quantification files and make a loop and stock every xlsx file

```{r}
# Path to quantifications
q_path <- "Data/Quantification/clean/"

# Make a list of all files names
list <- list.files(path = q_path, pattern = "xlsx")

# Initiate the loop
anatomy_full <- data.frame()

for(i in seq(1:length(list))){

    # Generate the row of ids
    temp_df <- extract_ids(list, i)

    # Extract data
    path = paste0(q_path, list[i])
    data_all <- extract_all(path)

    # Merge ids and data
    merged1 <- merge(temp_df, data_all)
    anatomy_full <- rbind(anatomy_full, merged1)
}

Plants <- read_csv("Data/Plants.csv")
Plants <- Plants[,c(2,4)]

Genotypes <- read.csv("Data/Genotypes.csv")
Genotypes <- subset(Genotypes, select = -X)

anatomy_full <- merge(x = anatomy_full, y = Plants,
                      by = "plant_id")

anatomy_full <- merge(x = anatomy_full, y = Genotypes[,c(2,3)],
                      by = "gen_id")
```

The file *anatomy_full* contains the parameters of GRANAR for each segment of each plant.

Export data :

```{r}
write.csv(anatomy_full, "Data/Anatomy.csv")
```

Create CS_id table

```{r}
CrossSections <- data.frame()

for(i in unique(anatomy_full$id)){
  temp <- anatomy_full %>% filter(id == i)
  temp <- temp[1,]
  temp_id <- paste0(temp$plant_id,
                    "_",
                    temp$segment,
                    "_",
                    temp$cut,
                    "_",
                    temp$zoom,
                    "_",
                    temp$repetition)

  tempDF <- data.frame(CS_id = c(temp_id),
                       plant_id = c(temp$plant_id),
                       segment = c(temp$segment),
                       cut = c(temp$cut),
                       zoom = c(temp$zoom),
                       repetition = c(temp$repetition))

  CrossSections <- rbind(CrossSections, tempDF)
}

write.csv(CrossSections,"Data/CrossSections.csv")
```

## Option 2 : Load CSV file with anatomic data

```{r}
anatomy_full <- read.csv("Data/Anatomy.csv")
anatomy_full <- anatomy_full[,-1] # remove first column

CrossSections <- read.csv("Data/CrossSections.csv")
CrossSections <- subset(CrossSections, select = -X)
```

# 2. GRANAR

## Import functions

GRANAR1 :

```{r}
# source("granar/io_function.R")
# source("granar/aer_in_geom_xml.R")
# source("granar/create_anatomy.R")
# source("granar/get_root_section.R")
source("granar/granar_metadata.R")
# source("granar/make_it3d.R")
# source("granar/plot_3d_root.R")
source("granar/plot_anatomy.R")
# source("granar/read_param_xml.R")
# source("granar/write_anatomy_obj.R")
source("granar/write_anatomy_xml_pv.R")
#source("granar/write_param_xml.R")
source("granar/write_param_xml2.R")
# 
# id = 1
# params_example <- data_all %>% filter(id == id)

```

GRANAR2 :

```{r}
# Load GRANAR2
source("granar/GRANAR6.R")
```

## Example of single GRANAR run

### Option 1 : from existing xml

```{r}
param_test <- read_param_xml("Params/A07_S3.xml")
```

### Option 2 : from the anatomy_full data

Write params into the folder Params

```{r}
for(i in unique(anatomy_full$id)){

  name <- paste0(unique(anatomy_full$plant_id[anatomy_full$id == i]),
                 "_",
                 unique(anatomy_full$segment[anatomy_full$id == i]))

  param_test <- anatomy_full %>% filter(id == i)
  param_test <- subset(param_test, select = c(name, type, value))
  t_path <- paste0("Params/", name, ".xml")
  write_param_xml2(param_test, t_path)
  }
```

### Run GRANAR

```{r}
sim <- create_anatomy(parameters =  param_test)

plot_anatomy(sim)


# write_anatomy_xml(sim = sim, path = "Anatomies/sim2.xml")
```

## Loop to generate cross sections

```{r}
for (i in unique(anatomy_full$id)){
  
  print(paste0("Generating anatomy ", i))
  
  # Extract data
  param_temp <- anatomy_full %>% filter(id == i)
  param_temp <- param_temp[c(7,8,9)]
  
  t <- data.frame(name = c("planttype"),
                   type = c("param"), 
                   value = c(2.0))
  
  
  param_temp <- rbind(param_temp, t)
  
  #write_to_xml
  
  try(TSim <- create_anatomy(parameters = param_temp))
  print("Anatomy successfully generated")
  
  plot_anatomy(TSim)
  
  TPath <- paste0("Anatomies/", i, ".xml")
  write_anatomy_xml(sim = TSim, path = TPath)
  
  
}
```

loop for the params in the file Params

```{r}
param_list <- list.files(path = "Params/", pattern = "xml")

for(i in param_list){
  temp_param <- read_param_xml(path = paste0("Params/", i ))
  sim <- create_anatomy(parameters = temp_param)
  plot_anatomy(sim)
}
```

# 
